\section{Conclusion}
\label{sec: conclusion}

This thesis employed a machine-learning technique to reconstruct temperature data at weather stations, offering a computationally lightweight alternative to Numerical Weather Prediction (NWP).
The approach was specifically designed to utilize only the ERA5 reanalysis data as input, making it universally applicable to any weather station worldwide.
Trained models for each station, based on convolution layers, effectively identified local patterns in the ERA5 data, resulting in more accurate temperature predictions compared to the ERA5 data itself.
Upon validation against test data, the models consistently outperformed the ERA5 data, showcasing varying levels of accuracy across different datasets.
Despite limitations in training data availability, the models successfully corrected both major and minor biases present in the ERA5 data. However, the correlation coefficient wise performance was more closely tied to the quantity of training data.
Notably, the model trained for the weather station in Barbados displayed promising capabilities in reconstructing the diurnal cycle, a feature not adequately represented in the ERA5 data despite being trained on only two years of data.

Looking forward to future research, various extensions for improvement and application can be explored.
One potential area is the incorporation of additional climate variables.
The weather stations of the 3D-PAWS network, for example, are equipped with a solar-radiation sensor. If only the temperature data is missing, the model could be trained to take besides the ERA5 temperature data, the solar radiation data as input. 

Although reconstruction is the pillar of this research, the ultimate goal is to deliver outstanding results to weather station operators, such as the 3D-PAWS team.
The thesis has developed an end-to-end software solution accompanied by a user-friendly web interface.
This interface enables the reconstruction of temperature data at any weather station globally without requiring extensive computer science knowledge.
It is crucial to note that the model's performance relies significantly on the quality and quantity of training data.
Hence, the software provides a platform for users to train and validate the model with their own data, accessible not only through the web interface but also automatically via the provided API.
Additionally, users can utilize the model's reconstruction results to assist in error-checking datasets by comparing them with actual measurements.
Subsequently, on the cleansed dataset, the model can be retrained, leading to improved accuracy.
The modularized design of the software allows for adjustments and extensions, such as incorporating different Reanalysis data sources.
Suppose another reanalysis dataset is more accurate for a specific region. In that case, the software can be configured to utilize this dataset instead of ERA5, with the models subsequently retrained on the new data.
Furthermore, it can be explored how the model can be applied to existing weather forecast data, such as that from the European Centre for Medium-Range Weather Forecasts (ECMWF) or the National Oceanic and Atmospheric Administration (NOAA).
This could be a promising approach to improve the local forecast quality, as the model represents knowledge of the local weather patterns.

In conclusion, the research presented in this thesis has demonstrated the potential of machine learning in reconstructing temperature data at weather stations in a computationally efficient and universally applicable manner.